Modelling the emergence of whisker barrels

### 2020-07-02 paper/briefpaper/brief.tex
Updated caption for whisker trim and a paragraph about the experiment

\MPthreePred{Add paragraph on whisker trimming here.}

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPthreePred{Simulating whisker trimming by reduction of
      $\epsilon$ for the thalamocortical projection for barrel C3, for which
      $i=13$. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{A} Graph of individual barrel measures
      plotted vs.~the multiplier applied to $\epsilon_{13}$. \textbf{B} The
      pattern for $\epsilon_{m}=0.64$.}}
  \label{fig:whiskertrim}
\end{center}

>>>>

\MPthreePred{To investigate the response of the model to environmental
  manipulation, we simulated a whisker deprivation experiment. In the first
  few days after birth, the upper region of the rat's cortex develops into
  distinct layers I--IV (layers V and VI are already distinct at
  birth). During this critical period, removal of the mystacial whiskers by
  electrocauterization, plucking or trimming leads to observable changes in
  brain structures, including the barrel field in cortical layer
  IV~\citep{jeanmonod_mouse_1981}. Amoung other changes, barrels associated
  with deprived whiskers have a smaller area. This is found whether the animal
  is deprived of an individual whisker~\citep{kossut_effects_1992}, or an
  entire row~\citep{loos_somatosensory_1973}, and demonstrates that
  thalamocortical activity contributes to the developmental process. We
  simulated the trimming of the individual whisker C3 during this critical
  period by reducing the amount by which its thalamocortical projections
  compete for branching. This was achieved by reducing the value of $\epsilon$
  in Eq.\,\ref{eq:comp} for the C3 projection, leaving other simulation
  parameters unchanged. The reduced competition for branching limited the area
  over which the C3 projection could make connections and its resulting barrel
  size was diminished (Fig.\,\ref{fig:whiskertrim}A). Its neighbours, whose
  ability to compete for branching was unchanged, were able to increase in
  size compared to the control simulation presented in Fig\,\ref{fig:main}C
  (Fig.\,\ref{fig:whiskertrim}B). The C3 barrel disappeared altogether if its
  competition parameter was reduced below a half of the original value.}

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPthreePred{Simulating whisker trimming by a reduction
      of the competition parameter, $\epsilon$, in the expression $\chi_i$
      (Eq.\,\ref{eq:comp}) for the C3 thalamocortical projection. For C3,
      $\epsilon$ is replaced by $m \epsilon$, where $m$ is a scalar
      multiplier. For the rest of the projections, $\chi_i$ is left unchanged
      and all other parameters are identical to those reported in
      Fig.\,\ref{fig:main}C. \textbf{A} The pattern formed after 30000 steps
      for $m=0.64$. Barrel C3 is reduced in size as its axon branching
      competes less strongly with its neighbours, whose area is slightly
      increased. \textbf{B} Individual barrel area plotted vs.~$m$
      shows that as $m$ is reduced, the area of C3 (blue squares) goes down,
      disappearing for $m\approx0.5$, whereas the average area of neighbouring
      barrels (triangles) increases.}}
  \label{fig:whiskertrim}
\end{center}
